Import_JazEmData

### 2024-03-27 Code/Import_JazEmData.Rmd
deleted variable name that no longer existed

# Join MulitiCulti par data with emission data
```{r join par with spectral data}
MC_SpectraPAR <- left_join(JazSpecTrim, MultiCultiPAR, by = c("WL" = "Actinic_nm", "SetPar_uE", "MC" = "MultiCulti")) %>%
  rename(MCSetPar_uE = 'SetPar_uE',
         MCMeasuredPar_uE = 'MeasuredPar_uE') %>% 
  select(-c(Par_ue, MultiCulti, Date))

>>>>

# Join MulitiCulti par data with emission data
```{r join par with spectral data}
MC_SpectraPAR <- left_join(JazSpecTrim, MultiCultiPAR, by = c("WL" = "Actinic_nm", "SetPar_uE", "MC" = "MultiCulti")) %>%
  rename(MCSetPar_uE = 'SetPar_uE',
         MCMeasuredPar_uE = 'MeasuredPar_uE') %>% 
  select(-c(MultiCulti, Date))
